### 2017-06-01 paper.tex
Editing down

Before re-using content,
make sure to check that the lesson is licensed in an open manner.
Both Programming Historian and the various Carpentry projects
use the Creative Commons - Attribution license
(see https://creativecommons.org/licenses/by/4.0/),
which allows people to share and adapt material for any purpose
as long as they cite the original source.

@@

An example of a particular lesson development practice is reverse instructional design
\cite{wiggins-mctighe}.
When this is used,
lessons are built by:

\begin{itemize}

\item
  identifying the learning objectives,

\item
  creating \emph{summative assessments} to determine whether those objectives have been met,

\item
  designing \emph{formative assessments} to gauge learners' progress
  and give them a chance to practice key skills,

\item
  putting those formative assessments in order,
  and

\item
  writing lessons to connect each to the next.

\end{itemize}

This methodology is effective in its own right,
but the real benefit comes when everyone understands what is supposed to happen
in what order.

Another example is Software Carpentry's instructor training program.
First offered in 2012,
this gradually turned into a two-day course delivered both in-person and online
\cite{lessons-learned}.
This crash course was a natural complement to Software Carpentry's regular workshops:
while the latter were created so that researchers wouldn't have to teach themselves how to program,
the former ensures that they don't have to teach themselves how to teach.
Instructor training now serves and an onboarding process to get everyone on the same page
regarding who lessons are for,
how they are delivered,
and how they are maintained.

@@

Similar to publishing software,
lessons should have releases of fixed content
so that learners or instructors who may wish to use the material have a stable version to refer to
for the duration of their use.
These releases should be periodic
so that improvements and adjustments are made available
for new learners and instructors just starting their use.
Periodic releases are also essential
for enabling recognition of the contribution of authors and maintainers.

The traditional academic system has limited ways of recognizing contributions.
Until systems have been expanded to improve this,
it is important to publish your lessons using a mechanism that provides recognition to the contributors.
Currently an effective way to do this is
to publish lessons with a DOI supplied by providers such as Zenodo (\url{https://zenodo.org/})
or DataCite (\url{https://zenodo.org/}).
Contributors can be listed as authors
and the maintainers of the lesson as editors
to provide differentiated recognition of their contributions.

A lesson release is a good opportunity to bring the material into a stable shape
by fixing outstanding issues and merging contribution.
The complete name and possible identifier like ORCID should also be gathered for every contributor.
Version control helps a lot in continuously maintaining a list of contributors
but also in remembering which version is used for release
(e.g., using branches or tags).
A lesson release is a permanent snapshot of the lesson
and it is recommended to use a consistent naming scheme from the beginning.
A convenient naming scheme is to use the full year and month of the release,
like ``2017.05'',
as it conveys a clear notion of date,
even to people that are new to the project.

Once the lesson is ready for release and has a name,
it should be built
and submitted to DOI supplier with its metadata,
such as lesson name, authors (e.g., contributors) and editors (e.g., maintainers).
Due to the collaborative aspect of the lesson development,
the number of authors and even lessons can grow very fast
and it is worth spending some time on automating this release process.
After the formal publishing,
it is also a good idea to publish the built lesson for direct access by the community,
making it clear which version is displayed and what is its corresponding DOI.

>>>>

Before re-using content,
make sure to check that the lesson is licensed in an open manner.
Both Programming Historian and the Carpentry projects
use the Creative Commons - Attribution license
(\url{https://creativecommons.org/licenses/by/4.0/}),
which allows people to share and adapt material for any purpose
as long as they cite the original source.

@@

An example of a particular lesson development practice is \emph{reverse instructional design}
\cite{wiggins-mctighe}.
When this is used,
lessons are built by
identifying learning objectives,
creating \emph{summative assessments} to determine whether those objectives have been met,
designing \emph{formative assessments} to gauge learners' progress
and give them a chance to practice key skills,
putting those formative assessments in order,
and only then writing lessons to connect each to the next.
This method is effective in its own right,
but its greatest benefit is that it gives everyone a common framework
within which to collaborate.

Another example is Software Carpentry's instructor training program.
First offered in 2012,
is now a two-day course delivered both in-person and online
\cite{lessons-learned}.
Not only does it teach good pedagogical practices,
it serves and an onboarding process to get everyone on the same page
regarding who lessons are for,
how they are delivered,
and how they are maintained.

@@

Like software,
lessons should have releases of fixed content
so that learners or instructors who may wish to use the material have a stable version to refer to
for the duration of their use.
These releases should be periodic
so that improvements and adjustments are made available
for new learners and instructors just starting their use.
Periodic releases are also essential
for enabling recognition of the contribution of authors and maintainers.

Academia has only a few ways of recognizing contributions.
Until these are expanded,
it is important to publish lessons in ways that traditional academic systems can digest.
One is to give particular releases of lessons
DOIs supplied by providers such as Zenodo (\url{https://zenodo.org/})
or DataCite (\url{https://zenodo.org/}).
Contributors can be listed as authors
and the maintainers of the lesson as editors
to differentiate recognition of their contributions.
Each time the lesson is published,
names and (where possible) identifiers like ORCIDs
should also be gathered for all contributors.

A lesson release is a good opportunity to bring the material into a stable shape
by fixing outstanding issues and merging contributions.
Version control helps a lot in continuously maintaining a list of contributors
but also in remembering which version is used for release
(e.g., using branches or tags).
Lesson releases should use a consistent naming scheme,
such as the full year and month of the release,
e.g. ``2017.05''.

If lessons are being released regularly,
it is worth automating this release process
with a simple shell script.
Old versions of lessons should be archived in a discoverable location for reference.
